\section{Tests}
\label{sec:tests}
The test are aimed to estimate the precision of the mount.
Of particular interest are the test using PHD2 which measure the precision in micro-adjustments for the auto-guiding system.

The application used to study the PHD2 plots is the PHD2LogViewer app.
The latter can upload all the guiding session you make, since every session is stored in the PHD2 folder.
The app also make raw statistical analysis which are good parameters to think about.
The root-mean-square (RMS) describe the spread of the data points around some average peak value (like standard deviation).
The value of RMS should be 1 arcsecond or lower for a good guiding.

\subsection{DEC V3 test}
The DEC V3 has been developed to reduce the mechanism backlash using the idea \textit{the less the number of belts gets, the better the guiding is}.
The resolution power of the mount is reported in table \ref{tab:resolution-power-DEC-V3}.
The extrapolated statistics is reported in table \ref{tab:DEC-V3-statistics}.
\\
\begin{minipage}
    {.5\textwidth}
    \begin{tabular}{ccc}
        Mechanism & microsteps (x360$^{\circ}$) & resolution (") \\
        \hline
        RA  & 19200 & 0.21\\ 
        DEC & 12800 & 0.65
    \end{tabular}
    \captionof{table}{Resolution power using the DEC V3 mechanism. Microsteps is intended as the total number of microsteps around the entire circumference.}
    \label{tab:resolution-power-DEC-V3}
\end{minipage}
\\
After the calibration, we have pointed the Rosetta nebula and start tracking.
The result can be seen in figure \ref{fig:guide-11-arcsec} and \ref{fig:guide-11-pixel}.
\\
\begin{minipage}{.4\textwidth}
    \centering
    \begin{tabular}{ccc}
        \textbf{Statistics}&RMS&Peak\\
        \hline
        RA& 0.47" (0.15 px)& 1.87" ( 0.58 px)\\
        DEC& 0.90" (0.28 px)&-8.12" (-2.52 px)\\
        Total& 1.02" (0.32 px)&\\
        \\
        \textbf{Drift}& ("/min) & (px/min)\\
        \hline
        RA& +3.01"/min& +0.94 px/min\\
        Dec& +2.14"/min& +0.66 px/min\\
        Polar Alignment Error& 8.7'&\\
        \hline
    \end{tabular}
    \captionof{table}{DEC V3 test: statistics of the guiding.}
    \label{tab:DEC-V3-statistics}
\end{minipage}